Perimeter Control of Swarms

### 2019-01-06 paper.tex

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to swarm coordination. Coordination of agent movement was proposed by Reynolds in his "Boid" model in 1987~\cite{REY:87}. This model uses a directional component based on neighbour orientation. The agents communicate with each other to determine a directional vector that is then applied to their movement. This technique has been extended by many authors to incorporate a more strategic advantage in the directional component of the swarms movement. Kawabayashi and Chen propsed an extended model that added predator avoidance and other bounds to make the movement more "organic" but did not add a goal based direction~\cite{KC:08}. Yao and Hwang used GPS signals to identify human movements to be boid-like~\cite{YH:14}.

>>>>

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to swarm coordination. Coordination of agent movement was proposed by Reynolds in his "Boid" model in 1987~\cite{REY:87}. This model uses a directional component based on neighbour orientation. The agents communicate with each other to determine a directional vector that is then applied to their movement. This technique has been extended by many authors to incorporate a more strategic advantage in the directional component of the swarms movement. Kawabayashi and Chen proposed an extended model that added predator avoidance and other bounds to make the movement more "organic" but did not add a goal based direction~\cite{KC:08}. Yao and Hwang used GPS signals to identify human movements to be boid-like~\cite{YH:14}. Kovacina et al. took the approach of allowing each agent to select a random direction, which was combined with the orientation of an agents neighbours as a mechanism to move a swarm~\cite{MPYV:02}, this is very similar to how the Boid model functions. The main problem with this approach is that although the swarm is directional there is no destination-based goal.
